Figure 7 - heterodimer

### 2024-08-08 ms_figure_7_heterodimer.Rmd
minor edits to (S)Fig7

(p_rel_dis <- ggplot(dist_ne, 
                     aes(x = SampleID, y = rel_distance_from_ne, 
                         fill = Condition)) + 
        geom_violin(trim = TRUE, bounds = c(0, 1)) +
        geom_signif(annotations = c(p_ntu1, p_ntu2),
                    xmin = c(1.5, 1.5), xmax = c(3.5, 5.5), 
                    y = c(1.05, 1.15),
                    tip_length = 0, step_increase = 0.1, parse = TRUE) + 
        geom_boxplot(width = 0.1, fill = "white") +
        labs(title = "Relative distance from nuclear envelope",
             x = "", y = "Distance from NE relative to radius") + 
        scale_fill_manual(values = c(na_color, main_colors[5], main_colors[1]),
                          name = "Condition") + 
        scale_x_discrete(labels = get_xlabs) +
        scale_y_continuous(breaks = c(0, 0.5, 1), limits = c(0, 1.2)) + 
        theme_cowplot() + 
        theme(axis.text.x = element_markdown(),
              legend.text = element_text(face = "italic")))
```

@@

(p_zone <- ggplot(zone_avg, aes(fill = Zone, y = 100 * avg_fraction_by_zone, 
                                x = Condition)) + 
     geom_bar(position = "stack", stat = "identity") +
     geom_text(aes(label = paste0(round(100 * avg_fraction_by_zone, 2), "%")), 
                   position = position_stack(vjust = 0.5), size = 4) +
     labs(title = "Relative zone distribution incl. both replicates", 
          x = "", y = "Relative distribution [%]") +
     scale_fill_manual(values = c(main_colors[1], main_colors[3], main_colors[5]),
                       name = "") + 
     scale_x_discrete(labels = get_xlabs_bar) + 
     theme_cowplot() + 
     theme(axis.text.x = element_markdown()))
```

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        gg_ipdimer, 
        fig7c,
        nrow = 1, 
        rel_widths = c(1, 2), 
        labels = c("A", "C"),
        align = "h", axis = "bt"
    ),
    cowplot::plot_grid(
        fig7b, 
        gcov,
        rel_widths = c(1, 1),
        labels = c("B", "D")
    ),
    cowplot::plot_grid(
        fig7e,
        NULL,
        fig7f,
        NULL,
        p_zone + theme(legend.position = "top"), 
        labels = c("E", "", "F", "", "G"),
        rel_widths = c(6, 0.75, 1.2, 0.75, 10.4), nrow = 1
    ), 
    ncol = 1
)
```

@@

cowplot::plot_grid(
    figs7a,
    cowplot::plot_grid(
        p_rel_dis,
        genomeplot_tpm,
        nrow = 1, 
        rel_widths = c(1, 1), 
        labels = c("B", "C")
    ),
    cowplot::plot_grid(
        genomeplot,
        gcovdel,
        nrow = 1, 
        rel_widths = c(1, 1),
        labels = c("D", "E")
    ),
    labels = c("A", "", ""), 
    ncol = 1, rel_heights = c(1, 1, 1)
)
```

>>>>

(p_rel_dis <- ggplot(dist_ne, 
                     aes(x = SampleID, y = rel_distance_from_ne, 
                         fill = Condition)) + 
        geom_violin(trim = TRUE, bounds = c(0, 1)) +
        geom_signif(annotations = c(p_ntu1, p_ntu2),
                    xmin = c(1.5, 1.5), xmax = c(3.5, 5.5), 
                    y = c(1.05, 1.15),
                    tip_length = 0, step_increase = 0.1, parse = TRUE) + 
        geom_boxplot(width = 0.1, fill = "white") +
        labs(x = "", y = "Distance from NE relative to radius") + 
        scale_fill_manual(values = c(na_color, main_colors[5], main_colors[1]),
                          name = "Condition") + 
        scale_x_discrete(labels = get_xlabs) +
        scale_y_continuous(breaks = c(0, 0.5, 1), limits = c(0, 1.2)) + 
        theme_cowplot() + 
        theme(axis.text.x = element_markdown(),
              legend.text = element_text(face = "italic")))
```

@@

(p_zone <- ggplot(zone_avg, aes(fill = Zone, y = 100 * avg_fraction_by_zone, 
                                x = Condition)) + 
     geom_bar(position = "stack", stat = "identity") +
     geom_text(aes(label = paste0(round(100 * avg_fraction_by_zone, 2), "%")), 
                   position = position_stack(vjust = 0.5), size = 4) +
     labs(x = "", y = "Relative zone distribution [%]") +
     scale_fill_manual(values = c(main_colors[1], main_colors[3], main_colors[5]),
                       name = "") + 
     scale_x_discrete(labels = get_xlabs_bar) + 
     theme_cowplot() + 
     theme(axis.text.x = element_markdown()))
```

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        gg_ipdimer, 
        fig7c,
        nrow = 1, 
        rel_widths = c(1, 2), 
        labels = c("A", "C"),
        align = "h", axis = "bt"
    ),
    NULL,
    cowplot::plot_grid(
        fig7b, 
        gcov,
        rel_widths = c(1, 1),
        labels = c("B", "D")
    ),
    NULL,
    cowplot::plot_grid(
        fig7e,
        NULL,
        fig7f,
        NULL,
        p_zone + theme(legend.position = "top"), 
        labels = c("E", "", "F", "", "G"), vjust = 2,
        rel_widths = c(6, 0.75, 1.2, 0.75, 10.4), nrow = 1
    ), 
    ncol = 1, rel_heights = c(1, 0.1, 1, 0.1, 1)
)
```

@@

cowplot::plot_grid(
    figs7a,
    NULL,
    cowplot::plot_grid(
        p_rel_dis,
        cowplot::plot_grid(genomeplot_tpm, NULL,
                           ncol = 1, rel_heights = c(1, 0.075)),
        nrow = 1, 
        rel_widths = c(1, 1), 
        labels = c("B", "C"),
        vjust = 0.5
    ),
    NULL,
    cowplot::plot_grid(
        genomeplot,
        gcovdel,
        nrow = 1, 
        rel_widths = c(1, 1),
        labels = c("D", "E"),
        vjust = 0.5
    ),
    labels = c("A", "", ""), 
    ncol = 1, rel_heights = c(1, 0.1, 1, 0.05, 1)
)
```
